\begin{titlingpage}
    \centering
    \vfill
    {\HUGE MONUMENT}\\[\baselineskip]
    {\Large SPRING 2023}\\[\baselineskip]
    {Edited by The Editor}\\[0.15\textheight]
    {Presented by the}\\[\baselineskip]
    {\Large CREATIVE WRITING CLUB}\\[\baselineskip]
    {of Haverhill High School}\\[\baselineskip]
    \vfill\null
\end{titlingpage}
\frontmatter

\clearpage
\tableofcontents
\clearpage

\mainmatter
\pagestyle{headings}
\setsecnumdepth{none}

\chapter{Exquisite Corpse Poems}

This is a description of the meaning of exquisite corpse

And perhaps a list of authors.

% TODO add \filbreak before titles
% Also figure out what that command does

\clearpage
\numerictitle{I}
\settowidth{\versewidth}{As I kneel at the grave of my father, do I wish I could take it back?}
\begin{verse}[\versewidth]
Rusted gold, weathering down, eroding in the silver wind\\
Light centering to a perfect dapple, illuminating the ground.\\
Shining from up above, only the gods can see me now\\
As I kneel at the grave of my father, do I wish I could take it back?\\
But where grief meets anger, I still feel nothing\\
The hollow of a vase, meant to sit, nothing to hold\\
But longing and desperation\\
Could never be undone.\\
A moment comes, a moment goes, forever all, forever one.\\
\end{verse}

\numerictitle{II}
\settowidth{\versewidth}{Silence after the pause, no noise to be heard but forever to be felt}
\begin{verse}[\versewidth]
Nostalgia always finds its way back to you,\\
Your scent, the touch of your woolen flannel \\
Softer than a spoken word\\
But still louder than everyone in the crowd.\\
The voice grows louder, deafening the surrounding silence\\
And then it stopped. \\
Silence after the pause, no noise to be heard but forever to be felt\\
The shock of it, a wild thing that cannot be controlled\\
But can be tamed by our past.\\
\end{verse}

\clearpage
\numerictitle{III}
\settowidth{\versewidth}{Ill intent causes forever broken trust in the mind of our own}
\begin{verse}[\versewidth]
Ill intent causes forever broken trust in the mind of our own\\
A circle that once cracked can only be patched with time\\
Like a heart break resembling the ache of loss\\
Figured in the shards of the cracked mirror\\
Whose desperate pieces shall never be decollated \\
Whose heart will never become whole again.\\
And though their heart has shattered into small fragments\\
Their head was still whole\\
But their body done, no more to give but their soul, which was the only thing that felt whole.\\
\end{verse}

\numerictitle{IV}
\settowidth{\versewidth}{Taken upon me to figure it out, through the forgetfulness of my thoughts}
\begin{verse}[\versewidth]
The brushed wings of the dove \\
Both sharp and ever delicate \\
But soft and hard at the same time.\\
There’s no two sides that are alike, no two sides that are the same\\
It simply is a trap, a paradox of mirrors and memories \\
Taken upon me to figure it out, through the forgetfulness of my thoughts\\
It’s too cold in my mind, how could lever meld myself together again?\\
The rays of sun no longer feel warm as I become the moon\\
But the moon, can be looked at by the naked eye \\
\end{verse}

\chapter{Assorted Writings}

\authorandtitle[McKaila Bushu]{Separated}
\settowidth{\versewidth}{Breaking, crying, wanting to scream cause it hurts tremendously}
\begin{verse}[\versewidth]
    Our love on two separate lanes, forever different but not truly and that’s what drives me insane\\
    Paper on the wet road\\
    Run over and stomped on\\
    Loving you, craving you just to leave was the perfect crime and I was your pon\\
    Gave you my heart\\
    All the faults I accepted when all you were was exceptionally disconnected\\
    Breaking, crying, wanting to scream cause it hurts tremendously \\
    I tried to go with it flexibly but why am i surprised you just followed your hurtful tendencies \\
    Our love now separated and divided till what we feel is the end of time \\
    Wanting to follow the little things \\
    Maybe it’s not actually over and maybe I need to follow those big signs\\ 
\end{verse}

\authorandtitle[Sasha Orr]{Raw}
\settowidth{\versewidth}{You tore in? Can the scope of all that is human}
\begin{verse}[\versewidth]
    Just soft enough to draw blood, \\
    Just harsh enough to pierce the skin, \\
    That inimitable sensation. \\
    Had you felt that clawing need too?\\
    Did you feel the soft pulse run through me as\\
    You tore in? Can the scope of all that is human \\
    Be surmised in a single act?\\
    The need to feel, relentless, no pulling back.   \\  
\end{verse}

\filbreak
\authorandtitle[Robert Frost]{Birches}
\begin{verse}
    When I see birches bend to left and right\\
    Across the lines of straighter darker trees,\\
    I like to think some boy’s been swinging them.\\
    But swinging doesn’t bend them down to stay\\
    As ice-storms do. Often you must have seen them\\
    Loaded with ice a sunny winter morning\\
    After a rain. They click upon themselves\\
    As the breeze rises, and turn many-colored\\
    As the stir cracks and crazes their enamel.\\
    Soon the sun’s warmth makes them shed crystal shells\\
    Shattering and avalanching on the snow-crust—\\
    Such heaps of broken glass to sweep away\\
    You'd think the inner dome of heaven had fallen.\\
    They are dragged to the withered bracken by the load,\\
    And they seem not to break; though once they are bowed\\
    So low for long, they never right themselves:\\
    You may see their trunks arching in the woods\\
    Years afterwards, trailing their leaves on the ground\\
    Like girls on hands and knees that throw their hair\\
    Before them over their heads to dry in the sun.\\
    But I was going to say when Truth broke in\\
    With all her matter-of-fact about the ice-storm\\
    I should prefer to have some boy bend them\\
    As he went out and in to fetch the cows—\\
    Some boy too far from town to learn baseball,\\
    Whose only play was what he found himself,\\
    Summer or winter, and could play alone.\\
    One by one he subdued his father's trees\\
    By riding them down over and over again\\
    Until he took the stiffness out of them,\\
    And not one but hung limp, not one was left\\
    For him to conquer. He learned all there was\\
    To learn about not launching out too soon\\
    And so not carrying the tree away\\
    Clear to the ground. He always kept his poise\\
    To the top branches, climbing carefully\\
    With the same pains you use to fill a cup\\
    Up to the brim, and even above the brim.\\
    Then he flung outward, feet first, with a swish,\\
    Kicking his way down through the air to the ground.\\
    So was I once myself a swinger of birches.\\
    And so I dream of going back to be.\\
    It’s when I’m weary of considerations,\\
    And life is too much like a pathless wood\\
    Where your face burns and tickles with the cobwebs\\
    Broken across it, and one eye is weeping\\
    From a twig’s having lashed across it open.\\
    I'd like to get away from earth awhile\\
    And then come back to it and begin over.\\
    May no fate willfully misunderstand me\\
    And half grant what I wish and snatch me away\\
    Not to return. Earth’s the right place for love:\\
    I don’t know where it's likely to go better.\\
    I'd like to go by climbing a birch tree,\\
    And climb black branches up a snow-white trunk\\
    Toward heaven, till the tree could bear no more,\\
    But dipped its top and set me down again.\\
    That would be good both going and coming back.\\
    One could do worse than be a swinger of birches.\\
\end{verse}

\clearpage
\authorandtitle[Keyton Castillo]{Cruel and Unusual Punishment}
\beginessay
When I was 12 years old, I remember that I was a calm guy and I liked to stay at home, and also never liked to go to parties. Perhaps this may sound weird to you, but I had many close friends with whom I grew up. My friends and  I used to play soccer,  I was lucky to meet them and stick with our friendship. However there’s a detail, my friends were popular, but I was not. As my friends were popular they used to know the girl I was in love with. Her name was Stacy, but I knew she would never give me a chance.

I used to live with my father in Costa Rica, the town’s name was San Rafael de Alajuela. My father has always been a serious, and strict man. He was that kind of father who gave you some occasional permission to do some things. My father hasn’t been lucky at all with women, and I believe that I inherited that from him. We lived in a small house, with two doors, one on the back and one on the front. I remember that there were more windows than doors. We had a small bathroom, and a window that I used to escape. I used to call this window my special window. My father didn’t know anything about this window, and if he knew about this window he would probably remove it. I was escaping through this window everytime that I wanted to go and play soccer with my friends, but this time the reason why I was going to escape was going to be different.

One Friday after school, my friends were planning to have a party on Saturday at 7 pm. They decided to invite me because they knew I was in love with Stacy and she would be at the party as well. How in the world would I miss this opportunity to just see her! But there was on challenge: gaining my father’s permission. I knew that my father wouldn’t let me go to that party because he was strict, but I wondered if I could do something to make him let me go? So, I decided to clean the whole house. So I washed the dishes, bathed the dog, I swept the floor, then I mopped the floor, even that day I didn’t eat anything so as not to dirty the dishes so when my father arrived at the house he would see the house clean. 

On Saturdays, my father used to go to a bar after a hard working day in construction. It was 4:30 pm, when my father arrived home, he saw that I did a nice job with the house, and that I had cleaned the house very well. He wrinkled his eyes and said “good job, Keyton.” Seeing him smiling and happy. I thought, well now is the time to ask him for permission. But I couldn’t summon the strength. I was still too scared of his answer. I was so scared, and I saw the door of his bedroom and it was as if it turned to rock, and in the rock was a dark hole, the rims of it lit by a fire surrounded by dangerous neanderthals, as if the door said “welcome to the cave”. Nonetheless, I somehow summoned the courage and blurted out: would it be alright if I went to Jose’s house for his party tonight?” But just as I feared ,his answer was a resounding “no”. 

I felt very upset, but I asked myself “ if I escape to go and play soccer with my friends, why would I not escape to go and see the girl I’m in love with?”

I decided to take a big risk, so I putted on the best clothes I had, and, as I had done many times, I climbed out my secret window.

I arrived at the party at 9 pm. I said hello to everyone, but I was looking for a specific person, and I found her. I didn’t find her the way I would like to find her, because she was already talking with somebody else, but I was thinking that he might be a friend. As the time passed it became more and more obvious that everyone was enjoying the party except me. It was almost 1 AM, and the party was going to end, and I saw my chance: maybe I could offer to walk her home and then come back”. When I approached her, she asked me if I could bring her something to drink, and of course I did.  Even though she only talked to me just to ask me for a favor I was elated, and I said this is the moment, I have my girl, I don’t care what my father is going to do to me, even if he is going to hit me, I don’t care, that’s not going to hurt me, because I have my girl. I was having a picture in my mind where after the party I was holding her hands, and telling her how much I loved her, and after that I saw myself kissing her. Then, having one of the best moments in my life with the girl that I had been in love with.               

But my dream, as exhilarating as it was, didn’t last long. As soon as I returned with her Coke, I saw her kissing the guy who she was talking with. I didn’t know how to feel, but the only thing I knew was that the big risk I took was worthless. The worst part was that the guy who she was talking to took her home, and I didn’t want to think what could have happened on the way, but I knew that my heart was broken. My friends laughed at first but then they told me “ don’t worry Keyton, there are more girls on the earth than stars in the sky”. 

You probably think that the situation could not have gotten any worse, but it did. Me and a friend were the last ones awake, telling some jokes about our childhood, and just when the situation started to get a little bit better for me, there was a cop behind me. He was looking for me because my father was scared because he thought that I was lost. The cop took me and dropped me to my father’s house. The only thing I knew was that my father was going to destroy me. When I arrived at my father’s house he was  looking at me, and he didn’t do anything to me, but I knew from his look that I was in trouble. 

The next day, on Sunday, he woke me up and told me that I had to work with him. He asked me what happened the day before, and I just told him the truth, and explained it all to him, because if I didn’t he would destroy me. He was really mad at me, but when he heard the story he didn’t get any madder, he just laughed and laughed. His laughter at my expense felt better than his disappointment and rage, so, all in all, I thought that that Sunday was going to be a good day, that I would be allowed to work and forget about what happened. But no, it only got worse.

My father and I ended up working at Stacy’s mother’s house. I didn’t know that he and Stacy’s mother were friends. To say the least I didn’t like to be there, but I knew that I had to because I had to fulfill my punishment.
